\chapter{Literature Review} \label{chap:literatureReview}

%\version{v1.10.2015}

\section*{}
In this chapter all of the concepts, theories and methods that are related with the management Information system such as system, information system and MIS will be discussed. The concept of educational management system is also well presented. In other sections the concept of EMIS will be considered in the world by especially focusing this concept in Pakistan will be discussed.This literature review gives us the idea to start our management thesis evaluation system so called management system in right direction.


\section{Management Information system}

There have been numerous kinds of systems that have been developed over the past several years. These information systems had helped to fulfil the needs and requirements of decision making not only at managerial but also at the operational level. Every organization develops its own management information system (MIS) which is totally dependent on the personal needs of the organizations. Management information system developed for one organization is useless for other organizations with different requirements 
\par In the management information system, not only the system itself is important but to get the maximum advantages from the system it is important that the human intelligence, perception and judgement must be powerful and strong enough to get combined with the system information.\par This combination will provide managers with the unique and valuable tool for the information management in any company.

\section{Management Information System}
Management system in this literature uses technique of having the directly accessible secure storage with well managed database.
Management Information system provides you the facility of your own need. It is a system which may be vary in every organization according to their needs or requirements. A system where data is collected and routed in desired locations where it is supposed to be and manage the data with getting desired results can be referred as management Information system. This gives us the idea to first make the database according to our desired need. Test that database with sample data so called dry run. Database is most essential and important part in any management system.Second thing that we get from this literature is that we need to know about the requirements in right direction. For this purpose we need to have in touch with the \textbf{DD PGP}.

\section{Educational Management Information System in World}

Educational management system in most of the countries is must needed now a days due to some of the following reason.

\textbf{Explosive growth of educational system}
\para This problem mentions the point that with growing student strength, management system in developing countries are compulsory to handle that much burden. This gives us the idea to make our management system power enough to cater with the university growing student strength and make it as efficient to use as we can.
\textbf{Low Cost Information Technology}
\para As technology is advancing now a days and we have lot of opportunity to get hardware as per our requirements. So this literature gives us the idea of having good hardware at low cost.

\section{Bahria University Online System ()}
\para Bahria university current online system is work on asp.net framework. Database used in this system is sql server and have accessible with Entity framework using LINQ. Bootstrap is used in front end interface to make it user friendly and beautiful. Current system is working on layers which means that it can be accessible on different levels with having different confidential access.

\section{Developer's Work}

After reading this research paper finally we are clear about the management systems that how it works and what things are need to be considered in development. Also we discussed here the Bahria University Online System because, we have to make Thesis Evaluation system on the level that we could embed it with the existing online system of University. So we have decided to work in asp.net (C#) with database Microsoft Sql server using Visual Studio.




