\chapter{Introduction} \label{chap:intro}

%\version{v1.11.2015}

\section*{}

MS/PhD Thesis Evaluation System will convert manual thesis system which includes paper work, to an automated system which does not need any paper work and where students, Professors, University Administration will interact by this automated system. This project is started on (Directorate Post
Graduate Program)’s request. Because of having too much problems in existing manually thesis system, Directorate PGP asked to make this system automated.



	\section{Problem Description}
	MS/PhD Thesis Evaluation System is basically designed to facilitate faculty members and the students, so that the students could interact with their supervisors through this system. The problem which arise here is that when students register for their thesis, they need to find out the supervisor of their choice. To cater with this problem we thought to give suggestion portion on system to suggest supervisor of their choice. After students suggestion,system’s administration side will decide whether that supervisor is available or not. If yes, then assign that supervisor to the relevant student otherwise assign by their choice.MS/PhD Thesis Evaluation System will be as secure as possible because all data of university students is involved in this process.
MS/PhD Thesis Evaluation System will be user friendly, so that students could use this system without any one’s special instructions.
	
	\section{Project Objectives}
	This project will automate the existing manually thesis system of Bahria University. This will resolve the existing problems and become a part of Bahria University Informational System. We are targeting university students and faculty members to make their thesis problem easier. 
	
	\section{Project Scope}
	The system at first stage is only made for Bahria University Islamabad Campus hence there is no distributed environment. But it can be enhanced and will be used in all other Campus of Bahria University. 

 \section{Feasibility Study}
We are able to meet our project schedule as per description.
\begin{enumerate}
\item Risks Involved: Main risk in this project is that, if we do something in our way without co-ordination in Director PGP, Director MIS then it can be very difficult and time consuming for us to change as per their requirements. To cater with this issue we will try our best to be in touch with them time to time.
\item Resource Requirement: Visual studio with SQL server and windows operating system is needed. Work space to work with peace of mind.
\end{enumerate}




